Twists of supersymmetric gauge theories

### 2019-12-04 paper.tex
Some 4d and 8d edits

\subsection{Dimension 8}
The 8-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^8$.  It has BRST fields given by a ghost, an 8d gauge field $A$, a pair of $\gg$-valued scalar fields $\phi_1$ and $\wt \phi_1$, and a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in S_+ \oplus S_-$.

In 8 dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
\begin{enumerate}
 \item Pure spinors, for which either $\lambda_+ = 0$ or $\lambda_- = 0$.  These supercharges are holomorphic.  They are stabilized by $\SU(4)$.  Twists by pure spinors can be made $\ZZ$-graded using a maximal torus in the R-symmetry group $\GL(1)$.
 \item Impure square-zero spinors with $\lambda_+ = 0$ or $\lambda_- = 0$.  These supercharges are topological.  They are stabilized by $\Spin(7) \sub \SO(8)$.  Again, twists by such supercharges can be made $\ZZ$-graded.
 \item Square-zero spinors where both $\lambda_+$ and $\lambda_-$ are non-zero.  Such supercharges have a 5-dimensional image in $\CC^8$.  Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
\end{enumerate}

\subsubsection{The Holomorphic and Topological Twists}
Square-zero supercharges in the 10d $\mc N=(1,0)$ supersymmetry algebra correspond to holomorphic supercharges in the 8d $\mc N=1$ supersymmetry algebra.  As such, we can calculate the holomorphic twist of 8d $\mc N=1$ super Yang-Mills by dimensionally reducing the holomorphic twist of 10d $\mc N=(1,0)$ super Yang-Mills along a copy of $\CC$.  This theory can, unlike its 10- and 9-dimensional analogues, be made canonically $\ZZ$-graded.

The holomorphic supercharge is stabilized by the group $\SU(4)$, and the topological supercharge is stabilized by $\spin(7)$.  If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$ \chris{check this claim: can we see it in terms of the Dynkin diagrams?}.  So, let's begin by establishing notation for the BRST fields of maximal super Yang-Mills after reduction to representations of various subgroups of $\SO(10)$.  We can write this schematically in the following way.

@@

Using this decomposition, we can describe the supersymmetric interaction terms $I^{(1)}$ and $I^{(2)}$ after reduction from 10d to 8d, with respect to various subgroups of $\mr O(8)$.  We begin by considering $\mr O(8)$ itself.

@@

@@

\subsubsection{The Rank 2 Twist}
We'll next discuss the example of the twist by a rank 2 spinor, where both $\lambda_+$ and $\lambda_-$ are non-zero.  We can understand this twist by a second application of Lemma \ref{CS_diml_red_prop} to the 9-dimensional $\mc N=1$ theory, or equivalently, by applying the lemma twice to the 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory.  This twisted theory is only $\ZZ/2\ZZ$-graded, just like its higher-dimensional counterparts.

@@

\vspace{-10pt}
\paragraph{Supersymmetry action:} Let $Q, Q_1$ and $Q_2$ be $\mc N=1$ supercharges.  We can describe the supersymmetry action as follows.
\begin{prop}
The supersymmetry action $I^{(1)} = I^{(1)}_{\mr{gauge}} + I^{(1)}_{\mr{matter}} + I^{(1)}_{\mr{couple}}$ and $I^{(2)} = I^{(2)}_{\mr{gauge}} + I^{(2)}_{\mr{matter}}$ from Section \ref{6d_10_section} restricts to 5-dimensional $\mc N=1$ fields as follows:
\begin{align*}
I^{(1)}_{\mr{gauge}}(Q) &= \int \\
I^{(1)}_{\mr{matter}}(Q) &= \int \\I^{(1)}_{\mr{gauge}}(Q) &= \int \\
I^{(2)}_{\mr{couple}}(Q_1,Q_2) &= \int  \\
I^{(2)}_{\mr{gauge}}(Q_1,Q_2) &= \int \\
I^{(2)}_{\mr{matter}}(Q_1,Q_2) &= \int 
\end{align*}
\end{prop}

\begin{proof}
\chris{...}
\end{proof}

@@

\subsubsection{$\mc N = 2$ Super Yang-Mills Theory}

@@

%
%The matter sector of the theory is labeled by the BRST fields:
%\begin{itemize}
%\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
%\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
%\end{itemize} 
%which together define the (abelian) local Lie algebra
%\[
%\mathcal E_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
%\]
%\subsection{Dimension 3}

>>>>

\subsection{Dimension 8}
\vspace{-10pt}
\paragraph{Fields:} 
The 8-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^8$.  It has BRST fields given by a ghost $c$ along with the following.
\begin{itemize}
 \item Bosons: an 8d gauge field $A$ in $\Omega^1(\RR^8; \gg)$, and a pair of $\gg$-valued scalar fields $\phi_1$ and $\wt \phi_1$ in $\Omega^0(\RR^8; \gg)$.
 \item Fermions: a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in \Omega^0(\RR^8; \gg \otimes(S_+ \oplus S_-))$.
\end{itemize}

We will see shortly that in the 8d $\mc N=1$ supersymmetry algebra there are holomorphic square-zero supercharges stabilized by the group $\SU(4)$, and topological square-zero supercharges stabilized by $\spin(7)$.  If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$ \chris{check this claim: can we see it in terms of the Dynkin diagrams?}.  So, let's begin by establishing notation for the BRST fields of maximal super Yang-Mills after reduction to representations of various subgroups of $\SO(10)$.  We can write this schematically in the following way.

@@

\vspace{-10pt}
\paragraph{Supersymmetry action:} 
Using the decomposition of the fields described above, we can describe the supersymmetric interaction terms $I^{(1)}$ and $I^{(2)}$ after reduction from 10d to 8d, with respect to various subgroups of $\mr O(8)$.  We begin by considering $\mr O(8)$ itself.

@@

\vspace{-10pt}
\paragraph{Twisting data:}
In 8 dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
\begin{enumerate}
 \item Pure spinors, for which either $\lambda_+ = 0$ or $\lambda_- = 0$.  These supercharges are holomorphic.  They are stabilized by $\SU(4)$.  Twists by pure spinors can be made $\ZZ$-graded using a maximal torus in the R-symmetry group $\GL(1)$.
 \item Impure square-zero spinors with $\lambda_+ = 0$ or $\lambda_- = 0$.  These supercharges are topological.  They are stabilized by $\Spin(7) \sub \SO(8)$.  Again, twists by such supercharges can be made $\ZZ$-graded.
 \item Square-zero spinors where both $\lambda_+$ and $\lambda_-$ are non-zero.  Such supercharges have a 5-dimensional image in $\CC^8$.  Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
\end{enumerate}

Square-zero supercharges in the 10d $\mc N=(1,0)$ supersymmetry algebra correspond to holomorphic supercharges in the 8d $\mc N=1$ supersymmetry algebra.  As such, we can calculate the holomorphic twist of 8d $\mc N=1$ super Yang-Mills by dimensionally reducing the holomorphic twist of 10d $\mc N=(1,0)$ super Yang-Mills along a copy of $\CC$.  This theory can, unlike its 10- and 9-dimensional analogues, be made canonically $\ZZ$-graded.

@@

We'll next discuss the example of the twist by a rank 2 spinor, where both $\lambda_+$ and $\lambda_-$ are non-zero.  We can understand this twist by a second application of Lemma \ref{CS_diml_red_prop} to the 9-dimensional $\mc N=1$ theory, or equivalently, by applying the lemma twice to the 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory.  This twisted theory is only $\ZZ/2\ZZ$-graded, just like its higher-dimensional counterparts.

@@

\vspace{-10pt}
\paragraph{Supersymmetry action:} Let $Q, Q_1$ and $Q_2$ be $\mc N=1$ supercharges.  We can describe the supersymmetry action as follows.
\begin{prop}
The supersymmetry action $I^{(1)} = I^{(1)}_{\mr{gauge}} + I^{(1)}_{\mr{matter}} + I^{(1)}_{\mr{couple}}$ and $I^{(2)} = I^{(2)}_{\mr{gauge}} + I^{(2)}_{\mr{matter}}$ from Section \ref{6d_10_section} restricts to 5-dimensional $\mc N=1$ fields as follows:
\begin{align*}
I^{(1)}_{\mr{gauge}}(Q) &= \int \\
I^{(1)}_{\mr{matter}}(Q) &= \int \\
I^{(2)}_{\mr{couple}}(Q_1,Q_2) &= \int  \\
I^{(2)}_{\mr{gauge}}(Q_1,Q_2) &= \int \\
I^{(2)}_{\mr{matter}}(Q_1,Q_2) &= \int 
\end{align*}
\end{prop}

@@

\subsubsection{$\mc N = 2$ Super Yang-Mills Theory} \label{5d_2_section}

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from section \ref{5d_2_section} to representations of the group $\mr O(4)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and six scalars, which we'll denote by $\phi \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))$.
 \item Fermions: four spinors, which we'll denote by $(\lambda_+ \otimes u_+, \lambda_- \otimes u_u) \in \Omega^0(\RR^5; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Supersymmetry action:} 
\begin{prop}
Consider a square-zero supercharge $Q = Q_+ \otimes w_+ + Q_- \otimes w_-$.  After reduction to $\mr O(4)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
\begin{align*}
I^{(1)}(Q) &= \int (\Gamma(Q_+, \lambda_-)(w_+,u_-), A^*) + (\Gamma(Q_-, \lambda_+)(w_-,u_+), A^*) + \langle Q_+, \lambda_+ \rangle (w_+ \wedge u_+, \phi^*) + \langle Q_-, \lambda_- \rangle (\omega(w_- \wedge u_-), \phi^*) + \\
&\quad + \frac12 \bigg( \langle \rho(F_A)Q_+, \lambda_+^*\rangle(w_+,u_+^*) + \langle \rho(F_A)Q_-, \lambda_-^*\rangle(w_-,u_-^*) +\\
&\qquad \qquad \qquad \qquad \langle\rho(\d_A (w_+ \wedge u_-^*,\phi))Q_+, \lambda_-^*\rangle + \langle\rho(\d_A (\omega(w_- \wedge u_+^*)),\phi)Q_-, \lambda_+^*\rangle \bigg),
\end{align*}
and
\begin{align*}
I^{(2)}(Q_1, Q_2) &= \int \frac 12 \left( g(\Gamma(Q_+, Q_-), \Gamma(\lambda^*_+, \lambda^*_-)) (w_+, w_-) (u_+^*,u_-^*) \right) + \\
&\quad - \frac 12 \big( \langle Q_+,\lambda_+^*\rangle^2(w_+,u_+^*)^2 + \langle Q_-,\lambda_-^*\rangle^2(w_-,u_-^*)^2 \big) - \langle Q_+,\lambda_+^*\rangle \langle Q_-, \lambda_-^*\rangle (w_+,u_+^*)(w_-,u_-^*) +\\
&\quad - (\langle Q_+, Q_+ \rangle (\omega^{-1}(w_+ \wedge w_+),\phi) + \langle Q_-, Q_- \rangle (w_- \wedge w_-,\phi)  ) c^*,
\end{align*}
where $\omega$ indicates the canonical isomorphism $\omega \colon \wedge^2(W^*) \to \wedge^2(W)$ (the Killing form for $\so(W^*)$).
\end{prop}
%
%The matter sector of the theory is labeled by the BRST fields:
%\begin{itemize}
%\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
%\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
%\end{itemize} 
%which together define the (abelian) local Lie algebra
%\[
%\mathcal E_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
%\]
%\subsection{Dimension 3}
